\part{The World}
\chapter{Terra-Prime}

\chapter{History}

\chapter{The Home-front Initiative}
\section{The Inventor}
The Inventor as one of the four 
\section{Doctor Insight}
\section{Captain Courage}
\section{New Home-front}
New Home-front is a newly created team of young superheroes and former sidekicks put together to focus on the local problems of the well so the older and more experienced heroes of the home-front initiative can focus on matters of interdimentional and galactic scale. The New Home-fronts roster is made up of Blink, Marvellous girl, Beeboy, Arcana, Miss aperture, Green jacket and Momentum. In terms of their roles not considering directly their individual unique powers and skills, Marvellous girl and Momentum functions as powerhouses, while Blink are the groups speedster. Beeboy is aerial support, while Miss aperture and green jacket have multiple situational abilities but can also do some control. Arcana is special in that she is extremely versatile because of her magic.
As a team they are still working out their internal communication, as they are all pretty young and lives together, it often involves a good portion of drama and emotions.
\subsection{Blink}
John Patricks is a special case, in that he was not just granted powers by the warp, but he is directly connected to the warp in a very unique way that gives him the properties of the primal portals that originally gave most people their powers. As he was found by Doctor Insight she helped him to understand his powers and be able to use them for good. It is clear that his connection with the warp goes beyond just being able to blink in and out of existence, but how so is more unclear. As part of the New home-front he is the groups fasted member. Blink started out as Doctor Insights side-kick and have always wanted to step out of her shadow and make a name for himself. This and his ego creates disruptions in young hero team. Blink insist that not only that he should be the leader of the group but is.z
\pagebreak 

\section{G.A.T.E.}
\subsection{Professor Enmity}
\pagebreak 



\section{The Black Regime}
\subsection{Alfather Brutalicus}
\pagebreak 

\section{The Hive}
\subsection{Queen Wasp}
\subsection{Drones}
\pagebreak 

\section{Basilisk}
\todo{Describe the Basilisk organization. Ninja order}
\subsection{Mistress Medusa}

\begin{tabular}{|c|c|c|c|}
\hline 
0 & 0 & 0 & 0 \\ 
\hline 
Str & Dex & Fgt & Awa \\ 
\hline 
0 & 0 & 0 & 0 \\ 
\hline 
Sta & Agi & Int & Pre \\ 
\hline 
\end{tabular} \\

\subsubsection{Powers:}

\textbf{Paralysing Stare:}
Mistress Medusa is not only a deadly assassin of high skill, but also have the petrifying power of being able to paralyse her opponents just with a stare. This effect can both be instant or delayed to take effect over time so the victim wont notice before its too late.\\

\textbf{Snake Physiology:}
Mistress Medusa is quick, alert and agile. Her body is athletic, flexible and she have a serpents tongue, which makes her a fearsome enemy both in social and combat encounters.\\

\section{The Starlight Academy}
\subsection{Headmaster Adam Black}
\textbf{Powers:}

\textbf{Astral Projection:}
Adam Black is able to separate his mind from his physical body and take on a astral form. This astral form can make itself visible to others in the physical world if be so wish. While in astral form he is able to travels great lengths almost instantly, and the astral form doesn't need any kind of life support, though his physical body do. While astral projecting the physical body goes into a hibernation state were the body needs are reduced but not negated. While astral projecting Adam Black's physical body is in a defenceless state.

\textbf{Hyper Empathy:}
Adam Black has an incredible ability to read people and their feelings. Adam's ability to read people are so precise that some people believe him to actually be able to read minds.